---
title: "CompileCSV"
author: "Luke Monroe"
date: "November 18, 2016"
output: html_document
---

This file creates plots based on CSV inputs in CompiledCSVs.



Initialize libraries
```{r Load yer modules, matey!}
require(shiny)
require(ggplot2)
require(ggrepel)
require(ggExtra)
require(plyr)
require(dplyr)
require(tidyr)
require(gridExtra)
require(reshape2)
require(RColorBrewer)
require(rstudioapi)
require(data.table)
```

Make sure to change basepath and the pertinent subfolders.  The paste(basepath, )
  method makes it harder to overwrite data from other runs, but make sure you
  change savedate and mastername as well, as the former affects serveroutput
```{r Ye best be definin' yer outputs}
histalpha <- 0.45
scatteralpha <- histalpha * 2/3
fluorlist <- c("FAM", "HEX", "Cy5")
  
welltotal <- 1024

basepath <- getwd()
  
serverinput = basepath
serveroutput = basepath
  
lappend <- function(lst, obj) {
  lst[[length(lst)+1]] <- obj
  return(lst)
}

linksubset <- 0
rowcolremove <- FALSE
```



Read in ALL DATA and modify it so it's ready for subsetting
```{r Create and prep Alldata}
Alldata <<- read.csv(file = "Compiled_Shiny_Data.csv", header = TRUE, sep = ",",
                     stringsAsFactors = FALSE)
Alldata <- subset(Alldata, select = -c(X))
```





FUNCTIONAL, OPTIONAL
  Shiny:  Uses "textInput".  Handles commas and colons! Might not need "rowcolremove"?
  
```{r Subset out bad rows and columns}
# Enter rows to subset.  Separate individual rows/columns with with commas
#   Denote sequences with ":"
rowSubsetInput <- "1, 2:4, 7"

colSubsetInput <- "1:3, 37, 62, 64"

texttonumeric <- function(stringinput) {
  
  # Remove spaces
  nospaces <- gsub(" ", "", stringinput)

  # If there's a comma, split around it.
  #   Make each element a new object in a vector
  nocommas <- c(sapply(nospaces, function(x)
                        if (grepl(",", x)) {
                            c(unlist(strsplit(x, ",")))
                        }
                )
          )

  # If there's a colon in any element of nocommas, it creates a sequence
  #   of numbers from the pre-colon number to the post-colon number
  nocolons <- c(unlist(lapply(nocommas, function(x)
                              if (grepl(":", x)) {
                                 storage <- c(seq(as.numeric(c(unlist(strsplit(x, ":"))))[1], 
                                                  as.numeric(c(unlist(strsplit(x, ":"))))[2], 1))
                              } else {
                                storage <- c(as.numeric(x))
                              }
            )))

  return(nocolons)
}

if (rowsubsetInput != "") {
  Alldata <- subset(Alldata, !(Row %in% texttonumeric(rowSubsetInput)))
  rowcolremove = TRUE
}

if (colsubsetInput != "") {
  Alldata <- subset(Alldata, !(Column %in% texttonumeric(colSubsetInput)))
  rowcolremove = TRUE
}

```






Plot the density curve of an array, then find the inflection point.
  Add this value to plotdata.
  For this plot, I'm defining the inflection point as the maximum value
  of the density's second derivative AFTER maximum density value
```{r Set limit based on max 2nd deriv after max den}
# Use the maximum value of the density's second derivative
#   larger the maximum value of the density to draw the line

max2deriv <- function(arrayID, fluor) {
  dendata <- subset(Alldata, ArrayID == arrayID)
  array <- dendata$Array[1]
  fluorcolumn <- grep(paste0(fluor,"AID"), colnames(dendata))
  fluorden <- density(dendata[, fluorcolumn], na.rm = TRUE)
    
  den <- data.frame(cbind(fluorden$x, fluorden$y))
  colnames(den) <- c("X", "Y")
  denmax <- den$X[match(max(den$Y, na.rm = TRUE), den$Y)]
    
  # Data frame of X and first derivative
  dydx <- data.frame(cbind(den$X[2:length(den$X)], differentiate(den$Y, den$X)))
  colnames(dydx) <- c("X", "dYdX")
  # Data frame of X and second derivative
  dydx2 <- data.frame(cbind(dydx$X[2:length(dydx$X)], differentiate(dydx$dYdX, dydx$X)))
  colnames(dydx2) <- c("X", "dYdX2")
  dydx2$X[match(max(subset(dydx2, X > denmax)$dYdX2, na.rm = TRUE), dydx2$dYdX2)]
}

assignlimits <- function(arrayID, fluor) {
  working <- subset(Alldata, ArrayID == arrayID)
  working <- mutate(working, limcol = max2deriv(arrayID, fluor))
  names(working)[names(working) == "limcol"] <- paste0(fluor, "lim")
  return(working)
}

FAMlims <- do.call(rbind, lapply(ArrayIDs, function(x)
                    assignlimits(x, "FAM")))$FAMlim
HEXlims <- do.call(rbind, lapply(ArrayIDs, function(x)
                    assignlimits(x, "HEX")))$HEXlim
Cy5lims <- do.call(rbind, lapply(ArrayIDs, function(x)
                    assignlimits(x, "Cy5")))$Cy5lim
Alldata <- cbind(Alldata, FAMlims, HEXlims, Cy5lims)
```




```{r Define subsets for your data before calling zygosity and plotting}
Tritonvals <- unique(Alldata$Triton)
Tweenvals <- unique(Alldata$Tween)
Mastervals <- unique(Alldata$Master)
RunDates <- unique(Alldata$RunDate)
RefMats <- unique(Alldata$RefMat)
CellStains <- unique(Alldata$CellStain)

numarrays <- function(identifier, value) {
  identifiercol <- grep(identifier, colnames(plotdata))
  length(unique(plotdata[plotdata[, identifiercol] == value, ]$ArrayID))
}

numTritonArrays <- sapply(unique(plotdata$Triton), function(x)
                                paste0(x, "%  (", numarrays("Triton", x), ")"))
numTweenArrays <- sapply(unique(plotdata$Tween), function(x)
                                paste0(x, "%  (", numarrays("Tween", x), ")"))
numMasterArrays <- sapply(unique(plotdata$Master), function(x)
                                paste0(x, "  (", numarrays("Master", x), ")"))
numRunDateArrays <- sapply(unique(plotdata$RunDate), function(x)
                                paste0(x, "  (", numarrays("RunDate", x), ")"))
numRefMatArrays <- sapply(unique(plotdata$RefMat), function(x)
                                paste0(x, "  (", numarrays("RefMat", x), ")"))
numCellStainArrays <- sapply(unique(plotdata$CellStain), function(x)
                                paste0(x, "  (", numarrays("CellStain", x), ")"))

selectInput('Triton', 'Triton Concentration', c(All='.', numTritonArrays))
selectInput('Tween', 'Tween Concentration', c(All='.', unique(plotdata$Tween)))
selectInput('Master', 'Silicon Master', c(All='.', unique(plotdata$Master)))
selectInput('RunDate', 'Run Date', c(All='.', unique(plotdata$RunDate)))
selectInput('RefMat', 'Reference Material', c(All='.', unique(plotdata$RefMats)))
selectInput('CellStain', 'Cell Stain', c(All='.', unique(plotdata$CellStain)))
selectInput('ArrayID', 'Array ID', c(All = '.', unique(plotdata$ArrayID)))


plotdata <- subset(Alldata, ArrayID = "2017_01_20_M3_Compiled")
```



This is the newer version of plotting scripts, as pulled from
  JointPlotter_2017-5-9_Cleaned.Rmd

Define calls for Zygosityplot and create graphs.  AID-filtered only
```{r Make Zygosity plot}
set1 <- brewer.pal(n = 9, "Set1")
set3 <- brewer.pal(n = 12, "Set3")
zygcolors <- c(set3[5], set3[10], set3[4])

# Define Zyg calls


callzygs <- function(array) {
  data <- subset(plotdata, Array == array)
  ampfluorcol <- grep(paste0(data$AmpFluor[1], "AID"), colnames(data))
  amplimscol <- grep(paste0(data$AmpFluor[1], "lims"), colnames(data))
  wtfluorcol <- grep(paste0(data$WTFluor[1], "AID"), colnames(data))
  wtlimscol <- grep(paste0(data$WTFluor[1], "lims"), colnames(data))
  mutfluorcol <- grep(paste0(data$MUTFluor[1], "AID"), colnames(data))
  mutlimscol <- grep(paste0(data$MUTFluor[1], "lims"), colnames(data))
  
  data$Zygosity[(data$CellGroup == 1 | data$CellGroup == "N/A") &
                  data[, ampfluorcol] >= data[, amplimscol] &
                  data[, wtfluorcol] >= data[, wtlimscol] &
                  data[, mutfluorcol] < data[, mutlimscol]] <- "WT"
  wt <- sum(data$Zygosity == "WT", na.rm = T)

  data$Zygosity[(data$CellGroup == 1 | data$CellGroup == "N/A") &
                  data[, ampfluorcol] >= data[, amplimscol] &
                  data[, mutfluorcol] >= data[, mutlimscol] &
                  data[, wtfluorcol] < data[, wtlimscol]] <- "MUT"
  mut <- sum(data$Zygosity == "MUT", na.rm = T)

  data$Zygosity[(data$CellGroup == 1 | data$CellGroup == "N/A") &
                  data[, ampfluorcol] >= data[, amplimscol] &
                  data[, mutfluorcol] >= data[, mutlimscol] &
                  data[, wtfluorcol] >= data[, wtlimscol]] <- "HET"
  het <- sum(data$Zygosity == "HET", na.rm = T)

  data$Zygosity <- factor(data$Zygosity, level=c("WT", "HET", "MUT"))
  
  return(data)
}

plotdata <- do.call(rbind, lapply(arraylist, function(x)
                              rbind(callzygs(x))))

zygosityplot <- function(array) {
  data <- subset(plotdata, Array == array)
  ampfluor <- data$AmpFluor[1]
  amplimscol <- grep(paste0(ampfluor, "lims"), colnames(data))
  mutfluor <- data$MUTFluor[1]
  mutlimscol <- grep(paste0(mutfluor, "lims"), colnames(data))
  wtfluor <- data$WTFluor[1]
  wtlimscol <- grep(paste0(wtfluor, "lims"), colnames(data))
  
  graph <- ggplot(data = na.omit(data),
         aes(x = Zygosity, fill = Zygosity), color = "black") +
    scale_fill_manual(values = zygcolors) +
    geom_bar() + geom_text(stat="count", aes(label=..count..), vjust=-0.5, size = 5) +
    labs(x = "Zygosity", y = "Count") + theme(legend.position = "none") +
    ggtitle(label = paste("Array", array, "Zygosities"),
          subtitle = paste0(ampfluor, ": ", round(data[1, amplimscol], 0),
                      "     ", wtfluor, ": ", round(data[1, wtlimscol], 0),
                      "     ", mutfluor, ": ", round(data[1, mutlimscol], 0)))
  return(graph)
}

zygosityplots <- do.call(arrangeGrob, c(lapply(arraylist, function(x)
                                                zygosityplot(x)), ncol = length(arraylist)))
```

Make pie charts for insertion into Zygosity PDF.  AID-filtered only
```{r Make Pie charts}
linksubset <- subset(plotdata, Linked != 0)

plotdata$Usable <- 0
plotdata <- mutate(plotdata, Usable=replace(Usable, !is.na(FAMAID),"Usable"))
plotdata <- mutate(plotdata, Usable=replace(Usable, is.na(FAMAID),"Unusable"))

  
  # Create fill stats by array
buildpiearray <- function(array) {
  newdf <- subset(plotdata, Array == array)
  ampfluorcol <- grep(paste0(newdf$AmpFluor[1], "AID"), colnames(newdf))
  amplimscol <- grep(paste0(newdf$AmpFluor[1], "lims"), colnames(newdf))
  wtfluorcol <- grep(paste0(newdf$WTFluor[1], "AID"), colnames(newdf))
  wtlimscol <- grep(paste0(newdf$WTFluor[1], "lims"), colnames(newdf))
  mutfluorcol <- grep(paste0(newdf$MUTFluor[1], "AID"), colnames(newdf))
  mutlimscol <- grep(paste0(newdf$MUTFluor[1], "lims"), colnames(newdf))
  welltotal <- nrow(newdf)
  nEmpty <- round(sum(newdf$Usable=="Unusable")*100/welltotal, 2)
  
  # Cell data calls
  n0Cells <- round(sum(newdf$Usable == "Usable" &
                         newdf$CellGroup == 0)*100/welltotal, 2)
  n1Cell <- round(sum(newdf$Usable == "Usable" &
                        newdf$CellGroup == 1)*100/welltotal, 2)
  nxCells <- round(sum(newdf$Usable == "Usable" &
                        newdf$CellGroup == "2 or more")*100/welltotal, 2)
  
  # Plasmid data calls
  nAmpNeg <- round(sum(newdf$Usable=="Usable" &
                         newdf$CellGroup=="N/A" &
                         newdf[, ampfluorcol] < newdf[, amplimscol],
                               na.rm = T)*100/welltotal, 2)
  nWT <- round(sum(newdf$Zygosity == "WT" &
                     newdf$CellGroup=="N/A",
                   na.rm = T)*100/welltotal, 2)
  nMUT <- round(sum(newdf$Zygosity == "MUT" &
                      newdf$CellGroup=="N/A",
                    na.rm = T)*100/welltotal, 2)
  nHET <- round(sum(newdf$Zygosity == "HET" &
                      newdf$CellGroup=="N/A",
                    na.rm = T)*100/welltotal, 2)
  noZyg <- round(sum(newdf$Usable == "Usable" &
                       newdf[, ampfluorcol] >= newdf[, amplimscol] &
                       is.na(newdf$Zygosity))*100/welltotal, 2)
  
  if (n0Cells != 0 | n1Cell != 0 | nxCells != 0) {
    piearray <- data.frame(paste("Array", array), nEmpty, n0Cells, n1Cell, nxCells)
    colnames(piearray) <- c("Array", "Empty", "% 0 Cells", "% 1 Cell", "% >1 Cell")
  } else {
    piearray <- data.frame(paste("Array", array), nEmpty, noZyg, nAmpNeg, nWT, nMUT, nHET)
    colnames(piearray) <- c("Array", "Empty", "% no Zyg", "% AmpNeg", "% WT", "% MUT", "% HET")
  }
  return(piearray)
}

piedflist <- list()
piedflist <- sapply(arraylist, function(x)
                  lappend(piedflist, buildpiearray(x)))

piedflist <- lapply(piedflist, function(x) melt(x))
piedflist <- lapply(piedflist, function(x)
                    mutate(x, yposition = 100-cumsum(value)+value/2))

cellpiecolors <- c(set1[7], set1[5], set1[3], set1[6])
plasmidpiecolors <- c(set1[7], set1[9], set1[8],
                      zygcolors[1], zygcolors[3], zygcolors[2])

pieplot <- function(array) {
  data <- subset(plotdata, Array == array)
  if (TRUE %in% grepl("Cells", piedflist[[array]]$variable)) {
    # Cell Data
    graph <- ggplot(piedflist[[array]],
                    aes(x = factor(1), y = value, fill = as.factor(variable))) +
      geom_bar(stat = "identity", width = 1) + coord_polar(theta = "y", direction = 1) + 
      geom_text_repel(aes(x = 1.6, y = yposition, label = value),
                      box.padding = unit(0.05, "lines"), size = 3) +
      labs(fill = "Array Yield") + scale_fill_manual(values = cellpiecolors) + 
      theme(axis.title=element_blank(), axis.text=element_blank(), axis.ticks=element_blank(),
            panel.grid=element_blank(), panel.spacing = unit(8.25, "lines"), legend.position = "left")
  } else {
    # Plasmid Data
    graph <- ggplot(piedflist[[array]],
                      aes(x = factor(1), y = value, fill = as.factor(variable))) +
      geom_bar(stat = "identity", width = 1) + coord_polar(theta = "y", direction = 1) + 
      geom_text_repel(aes(x = 1.6, y = yposition, label = value),
                      box.padding = unit(0.05, "lines"), size = 3) +
      labs(fill = "Array Yield") + scale_fill_manual(values = plasmidpiecolors) +
      theme(axis.title=element_blank(), axis.text=element_blank(), axis.ticks=element_blank(),
            panel.grid=element_blank(), panel.spacing = unit(8.25, "lines"), legend.position = "left")
  }
  return(graph)
}

pieplots <- do.call(arrangeGrob, c(lapply(arraylist, function(x)
                                        pieplot(x)), ncol = length(arraylist)))

```

Make stats table for insertion into Zygosity PDF.  AID-filtered only
```{r Make Stats tables}
stattable <- function(array) {
  newdf <- subset(plotdata, Array == array)
  nUsable <- nrow(subset(newdf, Usable == "Usable"))
  
  ampfluorcol <- grep(paste0(newdf$AmpFluor[1], "AID"), colnames(newdf))
  amplimscol <- grep(paste0(newdf$AmpFluor[1], "lims"), colnames(newdf))
  wtfluorcol <- grep(paste0(newdf$WTFluor[1], "AID"), colnames(newdf))
  wtlimscol <- grep(paste0(newdf$WTFluor[1], "lims"), colnames(newdf))
  mutfluorcol <- grep(paste0(newdf$MUTFluor[1], "AID"), colnames(newdf))
  mutlimscol <- grep(paste0(newdf$MUTFluor[1], "lims"), colnames(newdf))
    
  Amponly <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf[, ampfluorcol] >= newdf[, amplimscol] &
                  newdf[, mutfluorcol] < newdf[, mutlimscol] &
                  newdf[, wtfluorcol] < newdf[, wtlimscol], na.rm = TRUE)
  NoAmpHET <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf[, ampfluorcol] < newdf[, amplimscol] &
                  newdf[, mutfluorcol] >= newdf[, mutlimscol] &
                  newdf[, wtfluorcol] >= newdf[, wtlimscol], na.rm=TRUE)
  NoAmpMUT <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf[, ampfluorcol] < newdf[, amplimscol] &
                  newdf[, mutfluorcol] >= newdf[, mutlimscol] &
                  newdf[, wtfluorcol] < newdf[, wtlimscol], na.rm=TRUE)
  NoAmpWT <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf[, ampfluorcol] < newdf[, amplimscol] &
                  newdf[, mutfluorcol] < newdf[, mutlimscol] &
                  newdf[, wtfluorcol] >= newdf[, wtlimscol], na.rm=TRUE)
    
  TP <- sum(newdf$CellGroup == 1 &
              newdf[, ampfluorcol] >= newdf[, amplimscol], na.rm=TRUE)
  TN <- sum(newdf$CellGroup == 0 &
              newdf[, ampfluorcol] < newdf[, amplimscol], na.rm=TRUE)
  FP <- sum(newdf$CellGroup == 0 &
              newdf[, ampfluorcol] >= newdf[, amplimscol], na.rm=TRUE)
  FN <- sum(newdf$CellGroup == 1 &
              newdf[, ampfluorcol] < newdf[, amplimscol], na.rm=TRUE)
    
  # Plasmid data will have all 0's due to the CellGroup portion of TP/FP/FN/TN calling
  if (TP == 0 & FP == 0 & FN == 0 & TN == 0) {
    TP <- "N/A"
    TN <- "N/A"
    FP <- "N/A"
    FN <- "N/A"
    FD <- "N/A"
  } else {
    FD <- paste0(round(FP/(FP + sum(newdf$CellGroup == 1, na.rm=TRUE)), 3)*100, "%")
  }

  newarraystats <- data.frame(c(TP, TN, FP, FN, FD,
                              Amponly, NoAmpWT, NoAmpMUT, NoAmpHET),
                              stringsAsFactors = FALSE)
    
    # Don't try to apply the rounding function to plasmid data
  if (TP != "N/A") {
    percentstats <- lapply(newarraystats, function(x)
                            round(100*as.numeric(x)/nUsable,2))
  } else {
    percentstats <- lapply(newarraystats[c(6:9), 1], function(x)
                             round(100*as.numeric(as.character(x))/nUsable, 2))
    percentstats <- c(c(rep("N/A", 5)), c(unlist(percentstats)))
  }
  percentstats <- data.frame(c(unlist(percentstats)), stringsAsFactors = FALSE)

    
  colnames(newarraystats) <- c(paste("Array", array, "#"))
  colnames(percentstats) <- c(paste("Array", array, "%"))

  rownames(newarraystats) <- c("True Positive", "True Negative", "False Positive",
                                  "False Negative", "False Discovery", "Amp fluor only",
                                  "WT fluor only", "MUT fluor only", "WT & MUT only")
  rownames(percentstats) <- c("True Positive", "True Negative", "False Positive",
                                  "False Negative", "False Discovery", "Amp fluor only",
                                  "WT fluor only", "MUT fluor only", "WT & MUT only")
    
  if (length(linksubset) != 1 && nrow(linksubset) != 0) {
    nLinked <- data.frame(sum(newdf$Linked == 1), row.names = "Linked")
    colnames(nLinked) <- colnames(newarraystats)
    newarraystats <- rbind(newarraystats, nLinked)
    
    colnames(nLinked) <- colnames(percentstats)
    percentstats <- rbind(percentstats, round(nLinked/welltotal*100, 2))
  }
  return(cbind(newarraystats, percentstats))
}

stattables <- suppressWarnings(do.call(arrangeGrob, c(lapply(arraylist, function(x)
                                            tableGrob(stattable(x))),
                                     ncol = length(arraylist))))
```

Assemble disparate plots with grid.arrange
```{r Compile Zygosity, Pie and Stats and save to pdf}
plotwidth <- 3.5*length(arraylist)
plotheight <- 12

if (rowcolremove) {
  savestring <- paste0(savestring, "_RowColSubset")
}

setwd(serveroutput)
ggsave(paste0(savestring, "_Zygosity.pdf"),
              arrangeGrob(zygosityplots, pieplots, stattables,
                          nrow = 3,
                          heights = c(1/2, 1/4, 1/4)),
       width = plotwidth, height = plotheight)
```

















OLD VERSION THAT DOES NOT CALL FROM AMPFLUOR, MUTFLUOR AND WTFLUOR

Define calls for Zygosityplot and create graphs
```{r Make Zygosity plot}
plotcolors <- brewer.pal(n = 9, "Set1")

# Define Zyg calls
plotdata$Zygosity[(plotdata$CellGroup == 1 | plotdata$CellGroup == "N/A") &
                  plotdata$FAMAID >= plotdata$FAMlims &
                  plotdata$Cy5AID < plotdata$Cy5lims &
                  plotdata$HEXAID >= plotdata$HEXlims] <- "WT"
wt <- sum(plotdata$Zygosity == "WT", na.rm = T)

plotdata$Zygosity[(plotdata$CellGroup == 1 | plotdata$CellGroup == "N/A") &
                  plotdata$FAMAID >= plotdata$FAMlims &
                  plotdata$Cy5AID >= plotdata$Cy5lims &
                  plotdata$HEXAID < plotdata$HEXlims] <- "MUT"
mut <- sum(plotdata$Zygosity == "MUT", na.rm = T)

plotdata$Zygosity[(plotdata$CellGroup == 1 | plotdata$CellGroup == "N/A") &
                  plotdata$FAMAID >= plotdata$FAMlims &
                  plotdata$Cy5AID >= plotdata$Cy5lims &
                  plotdata$HEXAID >= plotdata$HEXlims] <- "HET"
het <- sum(plotdata$Zygosity == "HET", na.rm = T)

plotdata$Zygosity <- factor(plotdata$Zygosity)

zygosityplot <- function(array) {
  data <- subset(plotdata, Array == array)
  graph <- ggplot(data = na.omit(data),
         aes(x = Zygosity, fill = Zygosity), color = "black") +
    geom_bar() + geom_text(stat="count", aes(label=..count..), vjust=-0.5) +
    labs(x = "Zygosity", y = "Count") + theme(legend.position = "none") +
    ggtitle(label = paste("Array", array, "Zygosities"),
          subtitle = paste0("FAM: ", round(data$FAMlims[1], 0),
                            "     HEX: ", round(data$HEXlims[1], 0),
                            "     Cy5: ", round(data$Cy5lims[1], 0)))
  return(graph)
}

zygosityplots <- do.call(arrangeGrob, c(lapply(arraylist, function(x)
                                                zygosityplot(x)), ncol = 3))
```

Make pie charts for insertion into Zygosity PDF
```{r Make Pie charts}

plotdata$Usable <- 0
plotdata <- mutate(plotdata, Usable=replace(Usable, !is.na(FAMAID),"Usable"))
plotdata <- mutate(plotdata, Usable=replace(Usable, is.na(FAMAID),"Unusable"))
  
  # Create fill stats by array
buildpiearray <- function(array) {
  newdf <- subset(plotdata, Array == array)
  welltotal <- nrow(newdf)
  nEmpty <- round(sum(newdf$Usable=="Unusable")*100/welltotal, 2)
  
  # Cell data calls
  n0Cells <- round(sum(newdf$Usable == "Usable" & newdf$CellGroup == 0)*100/welltotal, 2)
  n1Cell <- round(sum(newdf$Usable == "Usable" & newdf$CellGroup == 1)*100/welltotal, 2)
  nxCells <- round(sum(newdf$Usable == "Usable" & newdf$CellGroup == "2 or more")*100/welltotal, 2)
  
  # Plasmid data calls
  nFAMNeg <- round(sum(newdf$Usable=="Usable" & newdf$CellGroup=="N/A" &
                         newdf$FAMPositive == 0, na.rm = T)*100/welltotal, 2)
  nWT <- round(sum(newdf$Zygosity == "WT" & newdf$CellGroup=="N/A", na.rm = T)*100/welltotal, 2)
  nMUT <- round(sum(newdf$Zygosity == "MUT" & newdf$CellGroup=="N/A", na.rm = T)*100/welltotal, 2)
  nHET <- round(sum(newdf$Zygosity == "HET" & newdf$CellGroup=="N/A", na.rm = T)*100/welltotal, 2)
  noZyg <- round(sum(newdf$Usable == "Usable" & newdf$FAMAID >= newdf$FAMlims & is.na(newdf$Zygosity))*100/welltotal, 2)
  
  if (n0Cells != 0 | n1Cell != 0 | nxCells != 0) {
    piearray <- data.frame(paste("Array", array), nEmpty, n0Cells, n1Cell, nxCells)
    colnames(piearray) <- c("Array", "Empty", "% 0 Cells", "% 1 Cell", "% >1 Cell")
  } else {
    piearray <- data.frame(paste("Array", array), nEmpty, noZyg, nFAMNeg, nWT, nMUT, nHET)
    colnames(piearray) <- c("Array", "Empty", "% no Zyg", "% FAMNeg", "% WT", "% MUT", "% HET")
  }
  return(piearray)
}

piedflist <- list()
piedflist <- sapply(arraylist, function(x)
                  lappend(piedflist, buildpiearray(x)))

piedflist <- lapply(piedflist, function(x) melt(x))
piedflist <- lapply(piedflist, function(x) mutate(x, yposition = 100-cumsum(value)+value/2))

cellpiecolors <- c(plotcolors[4:7])
plasmidpiecolors <- c(plotcolors[4], plotcolors[9], plotcolors[8], plotcolors[3:1])

if (linksubset != 0) {
  cellpiecolors <- c(cellpiecolors, plotcolors[9])
  plasmidpiecolors <- c(plasmidpiecolors, plotcolors[9])
}


pieplot <- function(array) {
  data <- subset(plotdata, Array == array)
  if (TRUE %in% grepl("Cells", colnames(piedflist[[array]]))) {
    # Plasmid Data
    graph <- ggplot(piedflist[[array]],
                      aes(x = factor(1), y = value, fill = as.factor(variable)),
                      color = "black") +
      geom_bar(stat = "identity", width = 1) + coord_polar(theta = "y", direction = 1) + 
      geom_text_repel(aes(x = 1.6, y = yposition, label = value),
                      box.padding = unit(0.05, "lines"), size = 3) +
      labs(fill = "Array Yield") + scale_fill_manual(values = plasmidpiecolors) +
      theme(axis.title=element_blank(), axis.text=element_blank(), axis.ticks=element_blank(),
            panel.grid=element_blank(), panel.spacing = unit(8.25, "lines"), legend.position = "left")
  } else {
    # Cell Data
    graph <- ggplot(piedflist[[array]],
                    aes(x = factor(1), y = value, fill = as.factor(variable)),
                    color = "black") +
      geom_bar(stat = "identity", width = 1) + coord_polar(theta = "y", direction = 1) + 
      geom_text_repel(aes(x = 1.6, y = yposition, label = value),
                      box.padding = unit(0.05, "lines"), size = 3) +
      labs(fill = "Array Yield") + scale_fill_manual(values = cellpiecolors) + 
      theme(axis.title=element_blank(), axis.text=element_blank(), axis.ticks=element_blank(),
            panel.grid=element_blank(), panel.spacing = unit(8.25, "lines"), legend.position = "left")
  }
  return(graph)
}

pieplots <- do.call(arrangeGrob, c(lapply(arraylist, function(x)
                                        pieplot(x)), ncol = length(arraylist)))

```

Make stats table for insertion into Zygosity PDF
```{r Make Stats tables}
stattable <- function(array) {
  newdf <- subset(plotdata, Array == array)
  nUsable <- nrow(subset(newdf, Usable == "Usable"))
    
  FAMonly <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf$FAMAID >= newdf$FAMlims &
                  newdf$Cy5AID < newdf$Cy5lims &
                  newdf$HEXAID < newdf$HEXlims, na.rm=TRUE)
  NoFAMHET <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf$FAMAID < newdf$FAMlims &
                  newdf$Cy5AID >= newdf$Cy5lims &
                  newdf$HEXAID >= newdf$HEXlims, na.rm=TRUE)
  NoFAMMUT <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf$FAMAID < newdf$FAMlims &
                  newdf$Cy5AID >= newdf$Cy5lims &
                  newdf$HEXAID < newdf$HEXlims, na.rm=TRUE)
  NoFAMWT <- sum((newdf$CellGroup == 1 | newdf$CellGroup == "N/A") &
                  newdf$FAMAID < newdf$FAMlims &
                  newdf$Cy5AID < newdf$Cy5lims &
                  newdf$HEXAID >= newdf$HEXlims, na.rm=TRUE)
    
  TP <- sum(newdf$CellGroup == 1 & newdf$FAMAID >= newdf$FAMlims, na.rm=TRUE)
  TN <- sum(newdf$CellGroup == 0 & newdf$FAMAID < newdf$FAMlims, na.rm=TRUE)
  FP <- sum(newdf$CellGroup == 0 & newdf$FAMAID >= newdf$FAMlims, na.rm=TRUE)
  FN <- sum(newdf$CellGroup == 1 & newdf$FAMAID < newdf$FAMlims, na.rm=TRUE)
    
  # Plasmid data will have all 0's due to the CellGroup portion of TP/FP/FN/TN calling
  if (TP == 0 & FP == 0 & FN == 0 & TN == 0) {
    TP <- "N/A"
    TN <- "N/A"
    FP <- "N/A"
    FN <- "N/A"
    FD <- "N/A"
  } else {
    FD <- paste0(round(FP/(FP + sum(newdf$CellGroup == 1, na.rm=TRUE)), 3)*100, "%")
  }

  newarraystats <- as.data.frame(c(TP, TN, FP, FN, FD,
                                     FAMonly, NoFAMWT, NoFAMMUT, NoFAMHET),
                                  nrow = 9, ncol = 1, stringsasfactors = FALSE)
    
    # Don't try to apply the rounding function to plasmid data
  if (TP != "N/A") {
    percentstats <- lapply(newarraystats, function(x) round(100*as.numeric(x)/nUsable,2))
  } else {
    percentstats <- lapply(newarraystats[c(6:9), 1],
                            function(x) round(100*as.numeric(as.character(x))/nUsable, 2))
    percentstats <- c(c(rep("N/A", 5)), c(unlist(percentstats)))
  }
  percentstats <- as.data.frame(unlist(percentstats),
                      nrow = nrow(newarraystats), ncol = 1, stringsasfactors = FALSE)

    
  colnames(newarraystats) <- c(paste("Array", array, "#"))
  colnames(percentstats) <- c(paste("Array", array, "%"))

  rownames(newarraystats) <- c("True Positive", "True Negative", "False Positive",
                                  "False Negative", "False Discovery", "FAM only",
                                  "HEX only", "Cy5 only", "HEX and Cy5 only")
  rownames(percentstats) <- c("True Positive", "True Negative", "False Positive",
                                  "False Negative", "False Discovery", "FAM only",
                                  "HEX only", "Cy5 only", "HEX and Cy5 only")
    
  if (linksubset != 0) {
    nLinked <- get(paste0("array", i, "linked"))
    nLinkExcluded <- nrow(subset(newdf, LinkExclude == "Exclude"))
      
    newarraystats <- rbind(newarraystats, as.numeric(nLinked))
    rownames(newarraystats)[length(rownames(newarraystats))] <- "Linked"
    newarraystats <- rbind(newarraystats, as.numeric(nLinkExcluded))
    rownames(newarraystats)[length(rownames(newarraystats))] <- "Link-Excluded"
      
    percentstats <- rbind(percentstats, round(100*nLinked/nUsable, 2),
                                          round(100*nLinkExcluded/nUsable, 2))
    rownames(percentstats) <- rownames(newarraystats)
  }
  return(cbind(newarraystats, percentstats))
}

stattables <- do.call(arrangeGrob, c(lapply(arraylist, function(x)
                                        tableGrob(stattable(x))), ncol = length(arraylist)))
```

Assemble disparate plots with grid.arrange
```{r Compile Zygosity, Pie and Stats and save to pdf}
plotwidth <- 3.5*length(arraylist)
plotheight <- 12

if (rowcolremove) {
  savestring <- paste0(savestring, "_RowColSubset")
}

setwd(serveroutput)
ggsave(paste0(savestring, "_Zygosity.pdf"),
              arrangeGrob(zygosityplots, pieplots, stattables,
                          nrow = length(arraylist),
                          heights = c(1/2, 1/4, 1/4)),
       width = plotwidth, height = plotheight)
```







New Zyg caller based on fluorescence, not CellGroup.  Use for LinkMap
```{r Write Zygosity Plotter CSV}
ZygCSV <- as.data.frame(subset(plotdata, select = c(Well, Array, CellGroup,
                                                    FAMAID, HEXAID, Cy5AID,
                                                    FAMlim, HEXlim, Cy5lim,
                                                    ArrayString, RightLinked)))

ZygCSV$FAMPositive <- 0
ZygCSV$HEXPositive <- 0
ZygCSV$Cy5Positive <- 0
ZygCSV <- mutate(ZygCSV, Usable=FAMAID)
ZygCSV <- ZygCSV %>% mutate(FAMPositive=replace(FAMPositive, FAMAID>=FAMlim,1))
ZygCSV <- ZygCSV %>% mutate(Cy5Positive=replace(Cy5Positive, Cy5AID>=Cy5lim,1))
ZygCSV <- ZygCSV %>% mutate(HEXPositive=replace(HEXPositive, HEXAID>=HEXlim,1))
ZygCSV <- ZygCSV %>% mutate(Usable=replace(Usable, !is.na(FAMAID),"Usable"))
ZygCSV <- ZygCSV %>% mutate(Usable=replace(Usable, is.na(FAMAID),"Unusable"))


plotcolors <- brewer.pal(n = 9, "Set1")

# Define Cell Zyg calls
ZygCSV$Zygosity[ZygCSV$FAMPositive == 1 &
                      ZygCSV$Cy5Positive == 0 & ZygCSV$HEXPositive == 1] <- "WT"
wt <- sum(ZygCSV$Zygosity == "WT", na.rm = T)

ZygCSV$Zygosity[ZygCSV$FAMPositive == 1 &
                  ZygCSV$Cy5Positive == 1 & ZygCSV$HEXPositive == 0] <- "MUT"
mut <- sum(ZygCSV$Zygosity == "MUT", na.rm = T)

ZygCSV$Zygosity[ZygCSV$FAMPositive == 1 &
                      ZygCSV$Cy5Positive == 1 & ZygCSV$HEXPositive == 1] <- "HET"
het <- sum(ZygCSV$Zygosity == "HET", na.rm = T)

ZygCSV$Zygosity <- factor(ZygCSV$Zygosity)
```

LinkMap
```{r Plot array-mimicking "map"}
#  %% = remainder, %/% = modulo
ZygCSV <- mutate(ZygCSV, Row = (Well-1) %/% 64 + 1)
ZygCSV <- mutate(ZygCSV, Column = (Well-1) %% 64 +1)

Testmap <- ggplot() + theme(legend.position = "left") +
  scale_x_continuous(minor_breaks = seq(4, 64, 4), breaks = seq(8, 64, 8)) +
  labs(x = "Column", y = "Row", color = "Zygosity", shape = "Cells in Wells", alpha = "Linked") +
  geom_point(data = ZygCSV, aes(Column, Row, shape = factor(CellGroup),
                                color=factor(Zygosity)), size = 3.5) +
  geom_point(data = subset(ZygCSV, RightLinked == 1), aes((Column+0.5), Row, alpha = RightLinked), size = 1.5) +
  ggtitle(paste(savestring, "Array Map"),
          subtitle="(Zygosity calls based on fluorescence alone)") + facet_grid(ArrayString~.) +
  scale_shape_manual(values = c(0, 16, 2, 18))


setwd(serveroutput)
pdf(paste(savestring, "_LinkMap.pdf", sep = ""), width = 10, height = 3.5*length(arraylist))
Testmap
dev.off()
```




Uses plotdata
LinkMap
```{r Plot array-mimicking "map"}
Testmap <- ggplot() + theme(legend.position = "left") +
  scale_x_continuous(minor_breaks = seq(4, 64, 4), breaks = seq(8, 64, 8)) +
  labs(x = "Column", y = "Row", shape = "Cells in Wells", alpha = "Linked") +
  geom_point(data = subset(plotdata, FAMAID >= 16000),
             aes(x = Column, y = Row, shape = factor(CellGroup)),
                                color="blue", size = 3.5) +
  geom_point(data = subset(plotdata, FAMAID < 16000),
             aes(x = Column, y = Row, shape = factor(CellGroup)),
                                color="red", size = 3.5) +
  ggtitle(paste(savestring, "Array Map"),
          subtitle="(FAM Positive Wells = blue)") + facet_grid(ArrayString~.) +
  scale_shape_manual(values = c(0, 16, 2, 18))

testhist <- ggplot() + geom_density(data = subset(plotdata, CellGroup == 0 & FAMAID > 16000),
                                      aes(x = Column), color = "red", alpha = 0.3) +
                        geom_density(data = subset(plotdata, CellGroup == 1 & FAMAID > 16000),
                                      aes(x = Column), color = "blue", alpha = 0.3) +
  facet_grid(.~Array)
testhist





```









                                    NOT YET CLEANED, BUT FUNCTIONAL
                                              OPTIONAL
PREPLOTTING LINKED EXCLUSION
Run this chunk if you want to remove data from wells that are linked.
If there are no cells in any of the linked wells, we can leave them - even
  though they share solution, there shouldn't be any reference material, so this
  shouldn't throw off our analysis.
If there is one well with cell(s), it removes all the other linked wells.
If there is more than one well with cell(s), it removes ALL linked wells in the chain.
```{r Include linkage information}
linkstart <- c()
linkstop <- c()

plotdata$RightLinked <- plotdata$Linked

# Build subset for observation, and for defining linkstart and linkstop
for (i in 2:(nrow(plotdata)-1)) {
  if (plotdata$Linked[i] == 1) {
    if (plotdata$Linked[i-1] != 1) {
      linkstart <- c(linkstart, i)
    }
    if (length(linksubset) == 1) {
      linksubset <- plotdata[i, ]
      linksubset <- rbind(linksubset, plotdata[i+1, ])
    } else {
      linksubset <- rbind(linksubset, plotdata[i, ])
      linksubset <- rbind(linksubset, plotdata[i+1, ])
    }
    if (plotdata$Linked[i+1] == 0) {
      linkstop <- c(linkstop, i+1)
    }
  }
}
linksubset <- unique(linksubset)

for (i in rownames(linksubset)) {
  plotdata$Linked[as.numeric(i)] <- 1
}


#   Use linkstart and linkstop to create row indices for examination.
#   This is more complicated than the fluor data because we (currently)
#     want to preserve data based on CellGroup
removallist <- c()
if (length(linkstart) > 0) {
  for (i in 1:length(linkstart)) {
    linkarray <- plotdata[linkstart[i]:linkstop[i], ]
    Celltotal <- 0
    Firstcell <- 0
    
    # Flag all linked plasmid wells for removal.
    #   Keep a running total of the number of linked wells with cells.
    for (j in 1:nrow(linkarray)) {
      if (linkarray$CellGroup[j] == "N/A") {
        removallist <- c(removallist, linkstart[i] + j - 1)
      } else if (linkarray$CellGroup[j] >= 1) {
        Celltotal <- Celltotal + 1
        if (Celltotal == 1) {
          Firstcell <- j
        }
      }
    }
    
    # If there's one cell total, remove everything else.
    #   If there's more, remove everything
    for (j in 1:nrow(linkarray)) {
      if (Celltotal == 1 && Firstcell != j) {
        removallist <- c(removallist, linkstart[i] + j - 1)
      } else if (Celltotal >1) {
        removallist <- c(removallist, linkstart[i] + j - 1)
      }
    }
  }
}


# Remove rows from plotdata that have indices in removallist
plotdata$LinkExclude <- "Include"
for (i in removallist) {
  plotdata$LinkExclude[i] <- "Exclude"
}

if (linksubset != 0) {
  array1linked <- nrow(subset(linksubset, Array == 1))
  array2linked <- nrow(subset(linksubset, Array == 2))
  array3linked <- nrow(subset(linksubset, Array == 3))
} else {
  array1linked <- 0
  array2linked <- 0
  array3linked <- 0
}

```






